---
title: "Business Analytics Assignment 1"
author: "SrushtiP"
date: "10/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1 A)

```{r}
pnorm(700, mean = 494, sd = 100, lower.tail = FALSE)
```
Probabbility of obtaining score greater than 700 is 0.01969927

Question 1 B)

```{r}
pnorm(450, mean = 494, sd = 100) - pnorm(350, mean = 494, sd = 100)
```
Probability of getting a score between 350 and 450 on the same GMAT exam is 0.2550349.

Question 2)

```{r}
Avg_per_dim_cost <- 449 - (qnorm(0.8665) * 36)
Avg_per_dim_cost
```
The average per diem cost in Buenos Aires is 409.0401

Question 3)

```{r}
Kent=c(59, 68, 78, 60) 
Los_Angeles=c(90, 82, 78, 75)

km <- mean(Kent)
lm <- mean(Los_Angeles)

numerator = sum((Kent - km)*(Los_Angeles - lm))
denomenator = sqrt(sum((Kent - km)^2)) * sqrt(sum((Los_Angeles- lm)^2))
Correlation <- numerator/denomenator

Correlation

cor(Kent, Los_Angeles)
```
Correlation is negative by 0.3566049

Read the data file.

```{r}
library(dplyr)
library(readr)

OR_object <- read_csv("Online_Retail.csv")
head(OR_object)
summary(OR_object)
```

Question 4)

```{r}
Total_Country_Transaction <- tapply(OR_object$InvoiceNo, OR_object$Country, NROW) / NROW(OR_object$InvoiceNo) * 100
subset(Total_Country_Transaction ,as.data.frame(Total_Country_Transaction) >1)
```
Countries accounting for more than 1% of the total transactions are EIRE, France, Germany, United Kingdom

Question 5)

```{r}
OR_object$TransactionValue <- OR_object$Quantity * OR_object$UnitPrice
summary(OR_object)
```

Question 6)

```{r}
Money_Spend <- aggregate(OR_object$TransactionValue, by = list(OR_object$Country), FUN = sum)
colnames(Money_Spend)<- c("Country", "Transaction_Value_Spend")
subset(Money_Spend, Money_Spend[2] > 130000)
```
Countries with total transaction exceeding 130,000 British Pound are Australia, EIRE, France, Germany, Netherlands, United Kingdom.

Question 7)

```{r}
Temp=strptime(OR_object$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
OR_object$New_Invoice_Date <- as.Date(Temp)
OR_object$New_Invoice_Date[20000]- OR_object$New_Invoice_Date[10]
OR_object$Invoice_Day_Week= weekdays(OR_object$New_Invoice_Date)
OR_object$New_Invoice_Hour = as.numeric(format(Temp, "%H"))
OR_object$New_Invoice_Month = as.numeric(format(Temp, "%m"))

head(OR_object)
summary(OR_object)
```

Question 7 A)

```{r}
tapply(OR_object$InvoiceNo , OR_object$Invoice_Day_Week, NROW) / NROW(OR_object$InvoiceNo) * 100
```

Question 7 B)

```{r}
tapply(OR_object$TransactionValue , OR_object$Invoice_Day_Week, sum) / sum(OR_object$TransactionValue) * 100
```

Question 7 C)

```{r}
tapply(OR_object$TransactionValue , OR_object$New_Invoice_Month , sum) / sum(OR_object$TransactionValue) * 100
```

Question 7 D)

```{r}
OR_object$New_Invoice_Date[max(OR_object$TransactionValue[OR_object$Country == "Australia"])]
```


Question 7 E)

```{r}
which.min(abs(diff(table(OR_object$New_Invoice_Hour), lag = 1, differences = 2)))
```

As the minimum value is for the 20th hour hence the store can be closed for maintenence between 6 PM to 8 PM

Question 8)

```{r}
Germany_Transaction <- subset(OR_object$TransactionValue, OR_object$Country == "Germany")
hist(Germany_Transaction, xlim = c (-600, 900), breaks = 100 , xlab = "Transaction Value of Germany", main = "Germany")
```

Question 9)

```{r}
NumberOfTransaction <- tapply(OR_object$TransactionValue,OR_object$CustomerID, length)
NumberOfTransaction[which.max(NumberOfTransaction)]

ValuableTransaction <- tapply(OR_object$TransactionValue,OR_object$CustomerID, sum)
ValuableTransaction[which.max(ValuableTransaction)]
```
Customer had the highest number of transactions is with CustomerID as 17841.
Most Valuable customer is with customerID 14646.

Question 10)

```{r}
colMeans(is.na(OR_object)) * 100
```

Question 11)

```{r}
NA_Sum <- function(input){
  Total_NA <- sum(is.na(input))
  return(Total_NA)
}

tapply(OR_object$CustomerID , OR_object$Country, NA_Sum)

```

Question 12)

```{r}

Customer_Visit_Count<-as.data.frame(table(OR_object$CustomerID))
colnames(Customer_Visit_Count)<-c("CustomerID","NumberOfVisits")
round(mean(abs(diff(Customer_Visit_Count$NumberOfVisits))))
```
Avgerage times a customer visits a store is 117 times.

```{r}
func <- function(x){
  y <- abs(diff.Date(x))
  z <- mean.difftime(x)
  return(z)
}
  
temp <- OR_object[order(OR_object$CustomerID),]
xyz <- aggregate(temp$New_Invoice_Date, by = list(temp$CustomerID), FUN = func)
View(xyz)

xyz <- unlist(xyz$x)
xyz<- xyz[xyz != 0]

round(mean(xyz)/(24*60))
```
On an average a customer returns to the online store after 11 days.

Question 13)

```{r}
NROW(OR_object$Quantity [OR_object$Quantity < 0 & OR_object$Country == "France"] ) / NROW(OR_object) * 100
```
Return rate for the French customers 0.02749539%

Question 14)

```{r}
Revenue<- aggregate(OR_object$TransactionValue, by = list(OR_object$Description), FUN = sum)
colnames(Revenue) <- c("Customer", "Revenue")
Revenue[which.max(Revenue$Revenue),]

```
The Dotcom Postage customer is most valuable customer with highest revenue.

Question 15)

```{r}
length(unique(OR_object$CustomerID))
```
There are 4373 unique customers in dataset.